Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-10 paper_jasa.tex
figure 2 caption

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.8in]{images/powerplot.pdf} 
   \caption{Comparison of probabilities to pick the actual data plot for different size lineups, $m$, and different values for data plot strength, $p_D$. The dashed  line, and grey 95\% pointwise confidence band, shows the probability of picking the data plot, by chance, if $H_0$ is true. }
   \label{fig:pval_power}
\end{figure}

>>>>

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.8in]{images/powerplot.pdf} 
   \caption{Probability that the data plot has the smallest probability in a lineup of size $m$. With increasing $p$-value the probability drops -- when it reaches $1/m$ a horizontal line is drawn to emphasize insufficient sensitivity of the test due to the lineup size. 
   %Comparison of probabilities to pick the actual data plot for different size lineups, $m$, and different values for data plot strength, $p_D$. The dashed  line, and grey 95\% pointwise confidence band, shows the probability of picking the data plot, by chance, if $H_0$ is true. }
}
   \label{fig:pval_power}
\end{figure}
